
\section{Introduction}
\pagenumbering{arabic}

The fishing industry plays a large role in the Scottish economy. Many rules and regulations have been put in place to improve the management of inshore fisheries in Scotland for sustainable fishing. The minimum landing size is an example of a simple regulation to protect breeding stock, not allowing any catches below the minimum size to be landed. This regulation ensures a proportion of the animal population continue to grow and reproduce \cite{masts-report} and is used particularly for inshore shellfisheries. Lobsters are an example of a family of crustaceans affected by the application of this regulation. 
\n
Typically, catches have to be sorted and measured manually in order to adhere to regulations on minimum landing size. Illegal and unwanted products are then discarded back to the sea. Rochet \cite{discard} notes that discarding continues to be an important problem in world fisheries as discarded products often do not survive. This defeats the purpose of the regulation to preserve breeding stock and further hurts the industry as discarded products are lost without economic gain. 
\n
There has been some research in the area of applying computer vision techniques to automatically identify and detect species of fish \cite{iobserver, fish-detection, fish-classification} and research into automatic measurement of fish size \cite{fish-size, fish-size2} which can be applied to reduce discarding. The detection of fish sizes is the first step in mitigation programs \cite{discard} to reduce discards, as Rochet states that a knowledge base on discarding patterns provides a basis for discussion on mitigation measures. Much work is focused on fish due to the impractical nature of manual observation and measurement. However, little work has been done that focuses on using such techniques and programmes for lobsters. 
\n
In this project, the application of subgraph matching and interest point detection is explored to automatically identify different parts of a lobster such as the claw, body or tail and from such identification, build a complete graph representation of a lobster. The proposed method uses an attributed graph, which represents the body parts as a set of nodes connected by weighted edges to represent the distance between the parts. This was done using a combination of computer vision techniques and probability models. The computer vision techniques identified relevant keypoints that the probabilistic models can label to build into subgraphs. The subgraphs are then matched and built into the complete graph with the same probability basis. Finally, analysis and evaluation was done to measure the performance and accuracy of the proposed methods. Using an existing dataset of lobster images gathered in collaborated with the Scottish Oceans Institute, this project is able to test and evaluate its methods against current attempts to determine the size and sex of the lobsters. TODO results brief

\subsection{Objectives}
Primary and secondary objectives of the project are listed below.
\subsubsection{Primary objectives}
\begin{itemize}
\item Explore and create suitable graph representations for lobsters
\item Match lobster subgraphs with complete graphs using existing software
\item Automatically detect interest points from images
\item Evaluate this method of graph matching on lobsters against the existing dataset
\end{itemize}
The objectives are vastly unchanged from the beginning of the project, but the objective \textit{match lobster subgraphs with complete graphs using existing software} has been changed from the original to better reflect what was done. Originally, the objective was to \textit{measure similarity of lobster graphs with existing software}. During the development of the project, this objective moved from the direction of using graph similarity to using subgraph isomorphism as a means of matching. Hence the original objective was changed to match the change in direction. 
\n
In this project, all primary objectives were met, resulting in a complete method which is able to take an image of a lobster from the dataset and:
\begin{itemize}
\item Detect interest points
\item Label interest points as lobster body parts
\item Create a graph representation from the detected points and labels
\item Match the graph representation to ideal models for evaluation
\end{itemize} 
The accuracy of the method was then analysed and evaluated. 
 
\subsubsection{Secondary objectives}
\begin{itemize}
\item Extend existing or come up with new algorithms for creating lobster graphs from images
\item Apply this technique on more complex images with noise such as natural lobsters in their environment
\item Apply this technique for video instead of images to give properties and information on the lobster in real time. 
\end{itemize}
Certain secondary objectives were touched upon and investigated during the design and implementation of this project, though none were explicitly explored. The ability to deal with noisy backgrounds was both noted and dealt with as an issue in the filtering (section \ref{sec:kp-filtering}) and combination (section \ref{sec:graph-creation}) stages respectively. The final method developed is a novel way to create a graph representation of a lobster from an image, combining a number of existing algorithms. 

